Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeast Taiwan

### 2019-11-01 analysis/paper/paper.Rmd
Momocs code worked!

```{r read-data}
library(here)
lf <- list.files(here("analysis", "data", "raw_data", "pottery_svg"), full.names = TRUE)

library(xml2)
library(stringr)
remove_scan_and_fill <- function(svg_file) {
  # remove the scan image from the SVG
  t1 <- read_xml(svg_file)
  t2 <- xml_children(t1)
  scan_layer <- t2[[4]]
  xml_remove(scan_layer)
  # now we have a SVG without the scan layer

  # change from outline to fill
  stroke_and_fill_node <- xml_children(t1)[4]
  stroke_and_fill_node_inner <- xml_children(stroke_and_fill_node)
  xml_attr(stroke_and_fill_node_inner, "style") <- 
    "fill:#000000;stroke:none;stroke-width:5;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"

write_xml(t1,
            str_glue("analysis/data/raw_data/fill_pottery_svg/fill_{basename(svg_file)}"))

  # fit image object to canvas in svg so it's all captured during the conversion to JPG
  system(str_glue('inkscape --verb=EditSelectAll --verb=AlignHorizontalCenter --verb=AlignVerticalCenter  --verb=FitCanvasToSelectionOrDrawing --verb=FileSave --verb=FileQuit "$(pwd)/analysis/data/raw_data/fill_pottery_svg/fill_{basename(svg_file)}"'))
}

# run the function on all SVGs
library(purrr)
walk(lf, remove_scan_and_fill)

# convert SVG to PNG
filled_svgs <- list.files("analysis/data/raw_data/fill_pottery_svg", pattern = "^fill_", full.names = TRUE)

# convert svgs to to jpg
library(magick)
library(rsvg)
map(filled_svgs,
  ~image_read_svg(.x) %>% 
  image_background("white") %>%  
  image_convert("jpg") %>% 
  image_write(str_glue("analysis/data/raw_data/pottery_jpg/{basename(.x)}_output.jpg")))
```

@@

# get list of jpgs only
jpgs <- list.files("analysis/data/raw_data/pottery_jpg", pattern = ".jpg", full.names = TRUE)

>>>>

@@

# get list of jpgs only
jpgs <- list.files("analysis/data/raw_data/outline_jpg", pattern = ".jpg", full.names = TRUE)
